## Setup

To follow the demonstrations of this presentation you will need [R](https://cran.r-project.org/bin/windows/base/) installed and an IDE like [R Studio](https://posit.co/products/open-source/rstudio) or [Positron](https://positron.posit.co/download.html).

And some R packages, please copy paste this code to make sure you have all the packages we need:

```{r, eval=FALSE}
install.packages(c(
  "CDMConnector", "duckdb", "CohortConstructor", "PhenotypeR", "gt", "visOmopResults",
  "ggplot2", "plotly", "flextable", "omock", "here"
))
```

In addition we will use synthetic OMOP CDM datasets to conduct the workshop. In order to download your data set in your laptop you must follow these steps:

- Create a folder: For example: '/Users/martics/Documents/OMOP/'

- Open your R environment file, run the following code in the console: 

```{r, eval=FALSE}
usethis::edit_r_environ()
```

- Write the following:

```
OMOP_DATA_FOLDER="path/to/your/folder"
```

- Restart R

```{r, eval=FALSE}
options(timeout = 600)
omock::downloadMockDataset(datasetName = "synpuf-1k_5.3")
omock::downloadMockDataset(datasetName = "delphi-100k_5.4")
```

If you are all set you should be able to run the following code:

```{r}
library(omock)
library(CohortConstructor)
library(PhenotypeR)

cdm <- mockCdmFromDataset(datasetName = "synpuf-1k_5.3", source = "duckdb")
cdm
```

::: {.callout-note collapse="true"}
## Alternative if you can not download 'synpuf-1k_5.3'

Alternatively you can connect to an smaller dataset: *GiBleed*

```{r}
cdm <- mockCdmFromDataset(datasetName = "GiBleed", source = "duckdb")
cdm
```
:::

## Alternative (use posit cloud)

Join posit cloud [here](https://posit.cloud/spaces/777897/join?access_code=hTqOr2YOVVQrdLz-AhTuCzD0DmnHwe-_3eNLwyie).
